The \dealii Library, Version 9.6

### 2024-09-24 9.6/paper.tex
Typo

    Since very early in the history of the library, the
    \texttt{AffineConstraints} class interface required building such
    constraints in multiple steps: First, one declared a degree of
    freedom as constrained; then one added the dependencies one after
    the other (e.g., by adding pairs $(\frac 12, 14)$ and $(\frac 12,
    15)$ in the hanging node example above); then one added
    inhomogeneities (by setting it to $42$ in the Dirichlet example
    above). This piecemeal approach is cumbersome and prevents the
    library from performing certain error checking steps because a
    constraint is not known to be completely built at any given point. The new
    \texttt{add\_constraint()} function now allows defining a
    constraint in one step.
  \item We refactored the systems for managing relative line and face
    orientations to significantly improve consistency across several library
    modules, including finite element classes, periodicity, and the
    \pfrst{} interface. \dealii{} has supported using unstructured
    three-dimensional meshes for a long time. Features like discontinuous
    Galerkin methods and higher-order elements require that lines and faces of
    adjacent elements are consistently oriented. For example, consider a line
    containing two degrees of freedom, which, in reference coordinates, are
    located at $x_1 = \frac 1 3$ and $x_2 = \frac 2 3$. If the line is read from
    left-to-right then we get points $(x_1, x_2)$ whereas if it is read from
    right-to-left we get $(x_2, x_1)$. \dealii{} guarantees that this order will
    be consistent across all cells sharing that line by storing a flag
    indicating whether (relative to the vertex enumeration on the present cell)
    that particular line is in the standard or reversed orientation. Faces in 3d
    are treated in a similar way. The only significant difference between lines
    and 3d faces is that, instead of two possible relative orientations,
    triangular faces have six and quadrilateral faces have eight
    possible orientation.

>>>>

    Since very early in the history of the library, the
    \texttt{AffineConstraints} class interface required building such
    constraints in multiple steps: First, one declared a degree of
    freedom as constrained; then one added the dependencies one after
    the other (e.g., by adding pairs $(\frac 12, 14)$ and $(\frac 12,
    15)$ in the hanging node example above); then one added
    inhomogeneities (by setting it to $42$ in the Dirichlet example
    above). This piecemeal approach is cumbersome and prevents the
    library from performing certain error checking steps because a
    constraint is not known to be completely built at any given point. The new
    \texttt{add\_constraint()} function now allows defining a
    constraint in one step.
  \item We refactored the systems for managing relative line and face
    orientations to significantly improve consistency across several library
    modules, including finite element classes, periodicity, and the
    \pfrst{} interface. \dealii{} has supported using unstructured
    three-dimensional meshes for a long time. Features like discontinuous
    Galerkin methods and higher-order elements require that lines and faces of
    adjacent elements are consistently oriented. For example, consider a line
    containing two degrees of freedom, which, in reference coordinates, are
    located at $x_1 = \frac 1 3$ and $x_2 = \frac 2 3$. If the line is read from
    left-to-right then we get points $(x_1, x_2)$ whereas if it is read from
    right-to-left we get $(x_2, x_1)$. \dealii{} guarantees that this order will
    be consistent across all cells sharing that line by storing a flag
    indicating whether (relative to the vertex enumeration on the present cell)
    that particular line is in the standard or reversed orientation. Faces in 3d
    are treated in a similar way. The only significant difference between lines
    and 3d faces is that, instead of two possible relative orientations,
    triangular faces have six and quadrilateral faces have eight
    possible orientations.
